### 2020-01-23 experiments.tex
rep

>>>>

We used the Universal Mutator \cite{universalmutator,regexpMut}, which aggressively produces large numbers of mutants, to generate all mutants.  We will make available a repository containing our full raw results plus details on contracts and projects selected, for replication and further analysis, upon acceptance (to avoid breaking blinding).
